\papertitle

### 2014-03-17 final-report/paper.tex
More to approach

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graphview}{Physical Query Plan View\xspace}
\newcommand*{\fragmentview}{Fragment Execution View\xspace}
\newcommand*{\networkview}{Worker Communication View\xspace}
\newcommand*{\overallview}{Fragment Overall View\xspace}

@@

We found that the performance of the query might be affected by the following
factors, which influenced :
\begin{itemize}
   \item 
\end{itemize}

>>>>

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

We found that the performance of the query might be affected by the following
factors, which greatly influenced the design of our visualization tool:
\begin{itemize}
   \item \emph{Wrong/unoptimized physical query plan.} We manually analyzed
several physical query plans and discovered that some queries were poorly
optimized. This led us to design a view that allows interactive exploration of
the physical query plan (mapped to a graph of query operators). 
   \item Stragglers, tail latency, expensive query operators, poor scheduling.
   \item Poor data partitioning, data skew.
\end{itemize}
